### 2024-07-02 Paper.tex
init

\documentclass[sigconf]{webmedia}
%webmeda.cls is adapted from acmart.cls for use in Proceedings of the Brazilian Symposium on Multimedia and the Web (WebMedia)

%%
%% \BibTeX command to typeset the BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\settopmatter{printacmref=false, printfolios=false}

%% Choose the appropriate event.
\setevent{webmedia}
\proceedingsDetails[WebMedia’2024]{Proceedings of the Brazilian Symposium on Multimedia and the Web}{2024}{Juiz de Fora, Brazil} 
\ISSN{XXXX-XXXX}

%\setevent{ctd}
%\proceedingsDetails[CTD’2024]{VI Concurso de Teses e Disserta{\c c}{\~o}es (CTD 2024). Anais Estendidos do XXX Simpósio Brasileiro de Sistemas Multimídia e Web}{2024}{Juiz de Fora/MG, Brazil} 
%\ISSN{2596-1683}

%\setevent{ctic}
%\proceedingsDetails[CTIC’2024]{IV Concurso de Trabalhos de Inicia{\c c}{\~a}o Cient{\'i}fica (CTIC 2024). Anais Estendidos do XXX Simpósio Brasileiro de Sistemas Multimídia e Web}{2024}{Juiz de Fora/MG, Brazil} 
%\ISSN{2596-1683}

%\setevent{wfa}
%\proceedingsDetails[WFA’2024]{XXII Workshop de Ferramentas e Aplica{\c c}{\~o}es (WFA 2024) (CTIC 2024). Anais Estendidos do XXX Simpósio Brasileiro de Sistemas Multimídia e Web}{2024}{Juiz de Fora/MG, Brazil} 
%\ISSN{2596-1683}

%% end of the preamble, the start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Insert Your Title Here}
\subtitle{Subtitle (optional)}
%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ben Trovato}
%\authornote{Both authors contributed equally to this research.}
\email{trovato@corporation.com}
\author{G.K.M. Tobin}
%\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin}
  \state{Ohio}
  \postcode{43017-6221}
}

\author{Lars Th{\o}rv{\"a}ld}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{larst@affiliation.org}

\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX\ document is presented as a
  paper formatted for publication in the proceedings of the WebMedia. Based on the ``acmart'' document class, this
  paper presents and explains the formatting elements an author may use to prepare his paper.
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{datasets, neural networks, gaze detection, text tagging}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{sampleteaser}
  \caption{Seattle Mariners at Spring Training, 2010.}
  \Description{Enjoying the baseball game from the third-base
  seats. Ichiro Suzuki preparing to bat.}
  \label{fig:teaser}
\end{teaserfigure}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}

If you are new to publishing with WebMedia, this document is a valuable
guide to preparing your work for publication. If you
have published with ACM before, this document provides insight and
instruction into more recent changes to the paper template.

The ``\verb|webmedia|'' document class must be used to prepare papers
for any stage
of publication, from review to final ``camera-ready'' copy, to the
author's own version, with {\itshape very} few changes to the source.

\section{Template Overview}
As noted in the introduction, the ``\verb|webmedia|'' document class must
be used to prepare your
double-blind initial submission of the paper.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

\subsection{Template Styles}

The primary parameter given to the ``\verb|webmedia|'' document class is
the {\itshape template style} which corresponds to the kind of publication. This parameter is enclosed in square
brackets and is a part of the {\verb|documentclass|} command:
\begin{verbatim}
  \documentclass[sigconf]{webmedia}
\end{verbatim}

WebMedia adopts the sigconf template style.

\subsection{Template Parameters}

In addition to specifying the {\itshape template style} to be used in
formatting your work, you must use the {\itshape template parameter} \verb|anonymous,review| for the ``double-blind'' submission. For ``double-blind'' submission, please use the following string as the first command in the
source file:
\verb|\documentclass[sigconf,anonymous,review]{webmedia}|.

\section{Modifications}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \verb|\vspace| command to manually adjust the
vertical spacing between elements of your work --- is not allowed.

{\bfseries Your document will be returned to you for revision if
  modifications are discovered.}

\section{Typefaces}

The ``\verb|webmedia|'' document class requires the use of the
``Libertine'' typeface family. Your \TeX\ installation should include
this set of packages. Please do not substitute other typefaces. The
``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
as they will override the built-in typeface families.

\section{Title Information}

The title of your work should use capital letters appropriately -
\url{https://capitalizemytitle.com/} has useful rules for
capitalization. Use the {\verb|title|} command to define the title of
your work. If your work has a subtitle, define it with the
{\verb|subtitle|} command.  Do not insert line breaks in your title.

If your title is lengthy, you must define a short version to be used
in the page headers, to prevent overlapping text. The \verb|title|
command has a ``short title'' parameter:
\begin{verbatim}
  \title[short title]{full title}
\end{verbatim}

\section{Authors and Affiliations}

Each author must be defined separately for accurate metadata
identification. Multiple authors may share one affiliation. Authors'
names should not be abbreviated; use full first names wherever
possible. Include authors' e-mail addresses whenever possible.

Grouping authors' names or e-mail addresses, or providing an ``e-mail
alias,'' as shown below, is not acceptable:
\begin{verbatim}
  \author{Brooke Aster, David Mehldau}
  \email{dave,judy,steve@university.edu}
  \email{firstname.lastname@phillips.org}
\end{verbatim}

The \verb|authornote| and \verb|authornotemark| commands allow a note
to apply to multiple authors --- for example, if the first two authors
of an article contributed equally to the work.

If your author list is lengthy, you must define a shortened version of
the list of authors to be used in the page headers, to prevent
overlapping text. The following command should be placed just after
the last \verb|\author{}| definition:
\begin{verbatim}
  \renewcommand{\shortauthors}{McCartney, et al.}
\end{verbatim}
Omitting this command will force the use of a concatenated list of all
of the authors' names, which may result in overlapping text in the
page headers.

The article template's documentation, available at
\url{https://www.acm.org/publications/proceedings-template}, has a
complete explanation of these commands and tips for their effective
use.

\section{Sectioning Commands}

Your work should use standard \LaTeX\ sectioning commands:
\verb|section|, \verb|subsection|, \verb|subsubsection|, and
\verb|paragraph|. They should be numbered; do not remove the numbering
from the commands.

Simulating a sectioning command by setting the first word or words of
a paragraph in boldface or italicized text is {\bfseries not allowed.}

\section{Tables}

The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

Table captions are placed {\itshape above} the table.

Because tables cannot be split across pages, the best placement for
them is typically the top of the page nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and the
table caption.  The contents of the table itself must go in the
\textbf{tabular} environment, to be aligned properly in rows and
columns, with the desired horizontal and vertical rules.  Again,
detailed instructions on \textbf{tabular} material are found in the
\textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table~\ref{tab:freq} is included in the input file; compare the
placement of the table here with the table in the printed output of
this document.

\begin{table}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math&Frequency&Comments\\
    \midrule
    \O & 1 in 1,000& For Swedish names\\
    $\pi$ & 1 in 5& Common in math\\
    \$ & 4 in 5 & Used in business\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \textbf{table*} to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more
desirable. Immediately following this sentence is the point at which
Table~\ref{tab:commands} is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table*}

\section{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of the three are
discussed in the next sections.

\subsection{Inline (In-text) Equations}
A formula that appears in the running text is called an inline or
in-text formula.  It is produced by the \textbf{math} environment,
which can be invoked with the usual
\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
and structures, from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
examples of in-text equations in context. Notice how this equation:
\begin{math}
  \lim_{n\rightarrow \infty}x=0
\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsection{Display Equations}
A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX\@; this section will just give a couple
of examples of display equations in context.  First, consider the
equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty}x=0
\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  \sum_{i=0}^{\infty} x + 1
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\section{Figures}

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{The 1907 Franklin Model D roadster.}
\end{figure}

Your figures should contain a caption which describes the figure to
the reader. Figure captions go below the figure. Your figures should
{\bfseries also} include a description suitable for screen readers, to
assist the visually-challenged to better understand your work.

Figure captions are placed {\itshape below} the figure.

\subsection{The ``Teaser Figure''}

A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Citations and Bibliographies}

The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

The bibliography is included in your source document with these two
commands, placed just before the \linebreak \verb|\end{document}| command:
\begin{verbatim}
  \bibliographystyle{ACM-Reference-Format}
  \bibliography{bibfile}
\end{verbatim}
where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
suffix, of the \BibTeX\ file.

Citations and references are numbered by default. A small number of
ACM publications have citations and references formatted in the
``author year'' style; for these exceptions, please include this
command in the {\bfseries preamble} (before \linebreak
``\verb|\begin{document}|'') of your \LaTeX\ source:
\begin{verbatim}
  \citestyle{acmauthoryear}
\end{verbatim}

  Some examples.  A paginated journal article \cite{Abril07}, an
  enumerated journal article \cite{Cohen07}, a reference to an entire
  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
  monograph/whole book in a series (see 2a in spec. document)
  \cite{Harel79}, a divisible-book such as an anthology or compilation
  \cite{Editor00} followed by the same example, however we only output
  the series if the volume number is given \cite{Editor00a} (so
  Editor00a's series should NOT be present since it has no vol. no.),
  a chapter in a divisible book \cite{Spector90}, a chapter in a
  divisible book in a series \cite{Douglass98}, a multi-volume work as
  book \cite{Knuth97}, an article in a proceedings (of a conference,
  symposium, workshop for example) (paginated proceedings article)
  \cite{Andler79}, a proceedings article with all possible elements
  \cite{Smith10}, an example of an enumerated proceedings article
  \cite{VanGundy07}, an informally published work \cite{Harel78}, a
  doctoral dissertation \cite{Clarkson85}, a master's thesis:
  \cite{anisi03}, an online document / world wide web resource
  \cite{Thornburg01, Poker06}, a video game (Case 1)
  \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and
  (Case 3) a patent \cite{JoeScientist001}, work accepted for
  publication \cite{rous08}, 'YYYYb'-test for prolific author
  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
  contain 'duplicate' DOI and URLs (some SIAM articles)
  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
  couple of citations with DOIs:
  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}.

\section{Acknowledgments}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the
preparation of the work should be included in an acknowledgment
section, which is placed just before the reference section in your
document.

This section has a special environment:
\begin{verbatim}
  \begin{acks}
  ...
  \end{acks}
\end{verbatim}
so that the information contained therein can be more easily collected
during the article metadata extraction phase, and to ensure
consistency in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.

\section{Appendices}

If your work needs an appendix, add it before the \linebreak
``\verb|\end{document}|'' command at the conclusion of your source
document.

Start the appendix with the ``\verb|appendix|'' command:
\begin{verbatim}
  \appendix
\end{verbatim}
and note that in the appendix, sections are lettered, not
numbered. This document has two appendices, demonstrating the section
and subsection identification method.

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\subsection{Part One}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
lacinia dolor. Integer ultricies commodo sem nec semper.

\subsection{Part Two}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
eros. Vivamus non purus placerat, scelerisque diam eu, cursus
ante. Etiam aliquam tortor auctor efficitur mattis.

\section{Online Resources}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
enim maximus. Vestibulum gravida massa ut felis suscipit
congue. Quisque mattis elit a risus ultrices commodo venenatis eget
dui. Etiam sagittis eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem
rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
massa et mattis lacinia.

\end{document}
\endinput
%%
%% End of file `sample-sigconf.tex'.

### 2024-07-02 Paper.tex
name defined

@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{Insert Your Title Here}
-\subtitle{Subtitle (optional)}
+\title{PAR Digital: Tecnologia em Prol do Ensino Inclusivo}
+
+% \subtitle{Subtitle (optional)}
 %%
@@
 %% used to denote shared contribution to the research.
-\author{Ben Trovato}
-%\authornote{Both authors contributed equally to this research.}
-\email{trovato@corporation.com}
-\author{G.K.M. Tobin}
-%\authornotemark[1]
-\email{webmaster@marysville-ohio.com}
+
+\author{Daniele Cássia}
 \affiliation{%
-  \institution{Institute for Clarity in Documentation}
-  \streetaddress{P.O. Box 1212}
-  \city{Dublin}
-  \state{Ohio}
-  \postcode{43017-6221}
-}
+  \institution{Departamento de Ciência de Computação}
+  \institution{Universidade Federal de Minas Gerais}
+  \city{Belo Horizonte}
+  \country{Brasil}}
+\email{danielecassia@ufmg.br}
 
-\author{Lars Th{\o}rv{\"a}ld}
-\affiliation{%
-  \institution{The Th{\o}rv{\"a}ld Group}
-  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
-  \city{Hekla}
-  \country{Iceland}}
-\email{larst@affiliation.org}
-
-\author{Valerie B\'eranger}
-\affiliation{%
-  \institution{Inria Paris-Rocquencourt}
-  \city{Rocquencourt}
-  \country{France}
-}
+\vspace{1cm}
 
@@
 %% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Trovato et al.}
+% \renewcommand{\shortauthors}{Trovato et al.}
 
@@
 %% article.
+
 \begin{abstract}
-  A clear and well-documented \LaTeX\ document is presented as a
-  paper formatted for publication in the proceedings of the WebMedia. Based on the ``acmart'' document class, this
-  paper presents and explains the formatting elements an author may use to prepare his paper.
+  Este artigo apresenta uma descrição dos objetivos e funcionalidades do
+  PAR Digital, demonstrando como o software pode transformar a prática
+  educacional inclusiva.
 \end{abstract}
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{datasets, neural networks, gaze detection, text tagging}
+\keywords{software, tecnologia, educação, plano educacional individualizado, inclusão}
 
@@
 %% page.
-\begin{teaserfigure}
-  \includegraphics[width=\textwidth]{sampleteaser}
-  \caption{Seattle Mariners at Spring Training, 2010.}
-  \Description{Enjoying the baseball game from the third-base
-  seats. Ichiro Suzuki preparing to bat.}
-  \label{fig:teaser}
-\end{teaserfigure}
+% \begin{teaserfigure}
+%   \includegraphics[width=\textwidth]{sampleteaser}
+%   \caption{Seattle Mariners at Spring Training, 2010.}
+%   \Description{Enjoying the baseball game from the third-base
+%   seats. Ichiro Suzuki preparing to bat.}
+%   \label{fig:teaser}
+% \end{teaserfigure}
 
@@
 
-\section{Introduction}
+\section{Introdução}
 
-If you are new to publishing with WebMedia, this document is a valuable
-guide to preparing your work for publication. If you
-have published with ACM before, this document provides insight and
-instruction into more recent changes to the paper template.
+O PAR Digital é uma ferramenta tecnológica desenvolvida com base em anos de estudo
+e pesquisa pela Faculdade de Educação da Universidade Federal de Minas Gerais, PAR
+significa Planejar, Aplicar, Rever, ações necessárias para que o ensino seja eficaz
+para os alunos com deficiência.
 
-The ``\verb|webmedia|'' document class must be used to prepare papers
-for any stage
-of publication, from review to final ``camera-ready'' copy, to the
-author's own version, with {\itshape very} few changes to the source.
+\section{Objetivo}
+O objetivo do PAR Digital é proporcionar uma ferramenta acessível e intuitiva 
+que facilite o preenchimento e a gestão do Plano Educacional Individualizado (PEI), 
+essencial para o desenvolvimento educacional dos alunos com deficiência. Desenvolvido
+ a partir de princípios do Desenho Universal de Aprendizagem (DUA) e de uma parceria 
+ com o Atendimento Educacional Especializado (AEE), o sistema visa integrar-se de 
+ maneira eficiente na rotina diária dos educadores, promovendo um ensino inclusivo 
+ e personalizado.
+% \url{https://www.acm.org/publications/proceedings-template}.
 
-\section{Template Overview}
-As noted in the introduction, the ``\verb|webmedia|'' document class must
-be used to prepare your
-double-blind initial submission of the paper.
+\section{Arquitetura}
 
-This document will explain the major features of the document
-class. For further information, the {\itshape \LaTeX\ User's Guide} is
-available from
-\url{https://www.acm.org/publications/proceedings-template}.
+A estrutura do projeto é organizada de maneira a facilitar a manutenção e a expansão 
+do mesmo.
 
-\subsection{Template Styles}
+As principais tecnologias utilizadas no projeto incluem React.js, uma biblioteca 
+JavaScript para construção de interfaces de usuário, escolhida por sua eficiência 
+na criação de componentes reutilizáveis e desempenho otimizado. O TypeScript é 
+usado para adicionar tipagem estática ao código JavaScript, aumentando a robustez 
+e facilitando a manutenção. O Redux é empregado para o gerenciamento de estado da 
+aplicação, ideal para aplicações de médio e grande porte que necessitam de um 
+controle mais sofisticado do estado. A biblioteca Material-UI é utilizada para 
+implementar o design system do Google Material Design, enquanto o Axios serve 
+como cliente HTTP para realizar requisições a APIs. Ferramentas como Jest e 
+React Testing Library são utilizadas para testes automatizados, garantindo a 
+qualidade e a funcionalidade do código.
 
-The primary parameter given to the ``\verb|webmedia|'' document class is
-the {\itshape template style} which corresponds to the kind of publication. This parameter is enclosed in square
-brackets and is a part of the {\verb|documentclass|} command:
-\begin{verbatim}
-  \documentclass[sigconf]{webmedia}
-\end{verbatim}
+O fluxo de dados na aplicação é gerenciado pelo Redux, que centraliza o estado da 
+aplicação em um único store. As ações são despachadas a partir dos componentes, 
+que são tratadas pelos `reducers` para atualizar o estado global. Essa abordagem 
+facilita a depuração e o desenvolvimento de novas funcionalidades, uma vez que o 
+estado da aplicação se torna previsível e controlado.
 
-WebMedia adopts the sigconf template style.
+A estilização da aplicação é feita utilizando CSS-in-JS com a biblioteca Material-UI,
+ permitindo uma aplicação consistente do design system através dos componentes. 
+ A utilização de temas facilita a customização e a manutenção do estilo visual da 
+ aplicação.
 
-\subsection{Template Parameters}
-
-In addition to specifying the {\itshape template style} to be used in
-formatting your work, you must use the {\itshape template parameter} \verb|anonymous,review| for the ``double-blind'' submission.
-For ``double-blind'' submission, please use the following string as the first command in the
-source file:
-\verb|\documentclass[sigconf,anonymous,review]{webmedia}|.
-
-\section{Modifications}
-
-Modifying the template --- including but not limited to: adjusting
-margins, typeface sizes, line spacing, paragraph and list definitions,
-and the use of the \verb|\vspace| command to manually adjust the
-vertical spacing between elements of your work --- is not allowed.
+Para a integração e entrega contínua (CI/CD), o projeto utiliza ferramentas como 
+o GitHub Actions, configurado para executar testes automatizados e builds a cada 
+commit, garantindo que a aplicação se mantenha estável e pronta para deployment. 
+O deploy é realizado em um servidor localizado na UFMG, permitindo uma escalabilidade
+ fácil e eficiente.
 
@@
 
-\section{Typefaces}
+\section{Funcionalidades}
 
@@
 
-\section{Title Information}
+\section{Licença}
+
+The title of your work should use capital letters appropriately -
+\url{https://capitalizemytitle.com/} has useful rules for
+capitalization. Use the {\verb|title|} command to define the title of
+your work. If your work has a subtitle, define it with the
+{\verb|subtitle|} command.  Do not insert line breaks in your title.
+
+If your title is lengthy, you must define a short version to be used
+in the page headers, to prevent overlapping text. The \verb|title|
+command has a ``short title'' parameter:
+\begin{verbatim}
+  \title[short title]{full title}
+\end{verbatim}
+
+\section{Perspectivas}
 

### 2024-07-08 Paper.tex
parte escrita para revisão

@@
 
-A estrutura do projeto é organizada de maneira a facilitar a manutenção e a expansão 
-do mesmo.
+A estrutura do projeto é organizada de maneira a facilitar 
+a manutenção e a expansão do mesmo.
 
@@
 
-Para a integração e entrega contínua (CI/CD), o projeto utiliza ferramentas como 
+Para a integração e entrega contínua (CI/CD), o projeto utiliza
 o GitHub Actions, configurado para executar testes automatizados e builds a cada
@@
 
-{\bfseries Your document will be returned to you for revision if
-  modifications are discovered.}
+% {\bfseries Your document will be returned to you for revision if
+%   modifications are discovered.}
 
@@
 
-The ``\verb|webmedia|'' document class requires the use of the
-``Libertine'' typeface family. Your \TeX\ installation should include
-this set of packages. Please do not substitute other typefaces. The
-``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
-as they will override the built-in typeface families.
+O projeto oferece diversas funcionalidades voltadas para o suporte
+educacional de estudantes com necessidades especiais. A seguir, são
+descritas as principais funcionalidades do sistema, cada uma desempenhando
+ um papel crucial na promoção de um ambiente inclusivo e eficaz para o
+ aprendizado
+
+\subsection{CRUD de Usuários}
+No sistema, os {\bfseries administradores} são responsáveis por gerenciar as
+escolas, visualizando relatórios e detalhes como professores e
+estratégias.
+% \begin{verbatim}
+%   \begin{teaserfigure}
+%     \includegraphics[width=\textwidth]{sampleteaser}
+%     \caption{figure caption}
+%     \Description{figure description}
+%   \end{teaserfigure}
+% \end{verbatim}
+% \begin{figure}[h]
+%   \centering
+%   \includegraphics[width=\linewidth]{sample-franklin}
+%   \caption{DANIELE}
+%   \Description{tENTANDO COLOCAR UMA IMAGEM AQUI.}
+% \end{figure}
+
+As {\bfseries escolas}  criam professores, responsáveis e
+desenvolvem o PEI, além de visualizar estratégias e dados dos alunos
+e professores.
+
+Os {\bfseries coordenadores}  acompanham o progresso dos alunos
+e estratégias, visualizando o andamento dos alunos.
+
+Os {\bfseries professores
+regulares}  são os usuários chave, criando e aplicando estratégias, e
+adicionando relatórios de progresso.
+
+Os {\bfseries professores AEE}  auxiliam
+os regulares, visualizando estratégias do PEI e relatórios, e
+participando de fóruns.
+
+Os {\bfseries responsáveis}  adicionam documentos
+necessários e acompanham o desenvolvimento dos alunos, visualizando
+seus dados e relatórios parciais.
+
+\subsection{Criação do PEI}
+A funcionalidade de criação do Plano Educacional Individualizado
+(PEI) é uma das mais importantes, permitindo que educadores e 
+coordenadores elaborem planos personalizados para atender às 
+necessidades específicas de cada aluno.
+
+\subsection{Estratégias do PEI}
+Dentro do PEI, os educadores podem definir e documentar diversas 
+estratégias pedagógicas adaptadas às necessidades do aluno. Essas 
+estratégias são orientações práticas que guiam os professores na 
+implementação do plano e ajudam a monitorar o progresso do aluno.
+
+\subsection{Relatório sobre Estratégias}
+A funcionalidade de relatórios permite que educadores e coordenadores 
+acompanhem o andamento das estratégias definidas no PEI. 
+Esses relatórios são fundamentais para avaliar o progresso do aluno, 
+identificar áreas que necessitam de ajustes e garantir que as 
+estratégias estão sendo eficazmente implementadas.
+
+\subsection{Fórum de Acompanhamento do Aluno}
+O fórum de acompanhamento do aluno é uma plataforma colaborativa onde 
+professores, coordenadores e outros profissionais podem discutir o 
+progresso do aluno, compartilhar insights e propor ajustes no PEI. 
+Este fórum promove uma abordagem colaborativa e integrada ao 
+acompanhamento educacional.
+
+\subsection{Reutilização de Estratégias}
+O sistema possui um banco de estratégias pedagógicas que podem ser 
+reutilizadas. Educadores podem consultar esse banco para encontrar 
+estratégias que já foram aplicadas com sucesso em situações similares
+, facilitando a implementação de práticas comprovadamente eficazes.
+
+\subsection{Compartilhamento de Recursos}
+Uma funcionalidade vital do PAR Digital é o compartilhamento de 
+recursos, especialmente Tecnologias Assistivas. Esse recurso 
+permite que professores e coordenadores acessem ferramentas e 
+materiais que podem ser utilizados para apoiar o aprendizado 
+dos alunos com necessidades especiais.
+
+\subsection{Perfil do Aluno}
+O sistema mantém um perfil detalhado do aluno, que inclui informações
+ educacionais e fundamentais. Esse perfil permite que educadores e 
+ coordenadores tenham uma visão abrangente das necessidades, 
+ capacidades e progressos do aluno, facilitando a personalização 
+ do ensino e a monitorização do desenvolvimento educacional.
 
 \section{Licença}
-
-The title of your work should use capital letters appropriately -
-\url{https://capitalizemytitle.com/} has useful rules for
-capitalization. Use the {\verb|title|} command to define the title of
-your work. If your work has a subtitle, define it with the
-{\verb|subtitle|} command.  Do not insert line breaks in your title.
-
-If your title is lengthy, you must define a short version to be used
-in the page headers, to prevent overlapping text. The \verb|title|
-command has a ``short title'' parameter:
-\begin{verbatim}
-  \title[short title]{full title}
-\end{verbatim}
+Software acadêmico, licença de tecnologias livres que está
+ sendo utilizado de forma de cunho social?
 
@@
 
-The title of your work should use capital letters appropriately -
-\url{https://capitalizemytitle.com/} has useful rules for
-capitalization. Use the {\verb|title|} command to define the title of
-your work. If your work has a subtitle, define it with the
-{\verb|subtitle|} command.  Do not insert line breaks in your title.
+\subsection{Perspectiva Acadêmica}
+O PAR Digital representa uma inovação significativa no campo 
+da educação inclusiva, oferecendo uma ferramenta tecnológica 
+poderosa para a gestão eficiente de Plano Educacional 
+Individualizado (PEI). Academicamente, essa ferramenta pode 
+servir como um catalisador para a pesquisa e o 
+desenvolvimento contínuo de estratégias pedagógicas 
+adaptativas.
 
-If your title is lengthy, you must define a short version to be used
-in the page headers, to prevent overlapping text. The \verb|title|
-command has a ``short title'' parameter:
-\begin{verbatim}
-  \title[short title]{full title}
-\end{verbatim}
+O acesso a dados detalhados sobre o progresso dos alunos, 
+bem como o compartilhamento de estratégias bem-sucedidas 
+entre os educadores, pode promover a produção de conhecimento
+ acadêmico relevante na área da educação inclusiva.
 
-\section{Authors and Affiliations}
+Além disso, o projeto pode facilitar estudos longitudinais 
+sobre o impacto de intervenções específicas no 
+desenvolvimento educacional de alunos com deficiência, 
+fornecendo insights valiosos para a comunidade acadêmica.
 
-Each author must be defined separately for accurate metadata
-identification. Multiple authors may share one affiliation. Authors'
-names should not be abbreviated; use full first names wherever
-possible. Include authors' e-mail addresses whenever possible.
+\subsection{Perspectiva Social}
+Socialmente, o PAR Digital tem o potencial de promover a 
+inclusão e a igualdade de oportunidades na educação. Ao 
+oferecer uma plataforma acessível e intuitiva para a 
+gestão de PEIs, o sistema capacita os educadores a 
+oferecer um suporte mais eficaz aos alunos com deficiência, 
+adaptando seus métodos de ensino às necessidades 
+individuais de cada estudante. Isso não apenas melhora 
+a experiência educacional desses alunos, mas também 
+fortalece a coesão social ao reconhecer e valorizar a 
+diversidade no ambiente escolar.
 
-Grouping authors' names or e-mail addresses, or providing an ``e-mail
-alias,'' as shown below, is not acceptable:
-\begin{verbatim}
-  \author{Brooke Aster, David Mehldau}
-  \email{dave,judy,steve@university.edu}
-  \email{firstname.lastname@phillips.org}
-\end{verbatim}
-
-The \verb|authornote| and \verb|authornotemark| commands allow a note
-to apply to multiple authors --- for example, if the first two authors
-of an article contributed equally to the work.
-
-If your author list is lengthy, you must define a shortened version of
-the list of authors to be used in the page headers, to prevent
-overlapping text. The following command should be placed just after
-the last \verb|\author{}| definition:
-\begin{verbatim}
-  \renewcommand{\shortauthors}{McCartney, et al.}
-\end{verbatim}
-Omitting this command will force the use of a concatenated list of all
-of the authors' names, which may result in overlapping text in the
-page headers.
-
-The article template's documentation, available at
-\url{https://www.acm.org/publications/proceedings-template}, has a
-complete explanation of these commands and tips for their effective
-use.
-
-\section{Sectioning Commands}
-
-Your work should use standard \LaTeX\ sectioning commands:
-\verb|section|, \verb|subsection|, \verb|subsubsection|, and
-\verb|paragraph|. They should be numbered; do not remove the numbering
-from the commands.
-
-Simulating a sectioning command by setting the first word or words of
-a paragraph in boldface or italicized text is {\bfseries not allowed.}
-
-\section{Tables}
-
-The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
-package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
-high-quality tables.
-
-Table captions are placed {\itshape above} the table.
-
-Because tables cannot be split across pages, the best placement for
-them is typically the top of the page nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and the
-table caption.  The contents of the table itself must go in the
-\textbf{tabular} environment, to be aligned properly in rows and
-columns, with the desired horizontal and vertical rules.  Again,
-detailed instructions on \textbf{tabular} material are found in the
-\textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table~\ref{tab:freq} is included in the input file; compare the
-placement of the table here with the table in the printed output of
-this document.
-
-\begin{table}
-  \caption{Frequency of Special Characters}
-  \label{tab:freq}
-  \begin{tabular}{ccl}
-    \toprule
-    Non-English or Math&Frequency&Comments\\
-    \midrule
-    \O & 1 in 1,000& For Swedish names\\
-    $\pi$ & 1 in 5& Common in math\\
-    \$ & 4 in 5 & Used in business\\
-    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-  \bottomrule
-\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \textbf{table*} to enclose the table's
-contents and the table caption.  As with a single-column table, this
-wide table will ``float'' to a location deemed more
-desirable. Immediately following this sentence is the point at which
-Table~\ref{tab:commands} is included in the input file; again, it is
-instructive to compare the placement of the table here with the table
-in the printed output of this document.
-
-\begin{table*}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command &A Number & Comments\\
-    \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
-    \bottomrule
-  \end{tabular}
-\end{table*}
-
-\section{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of the three are
-discussed in the next sections.
-
-\subsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an inline or
-in-text formula.  It is produced by the \textbf{math} environment,
-which can be invoked with the usual
-\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
-the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
-and structures, from $\alpha$ to $\omega$, available in
-\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
-examples of in-text equations in context. Notice how this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty}x=0
-\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsection{Display Equations}
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \textbf{equation}
-environment. An unnumbered display equation is produced by the
-\textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols and
-structures available in \LaTeX\@; this section will just give a couple
-of examples of display equations in context.  First, consider the
-equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty}x=0
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  \sum_{i=0}^{\infty} x + 1
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\section{Figures}
-
-The ``\verb|figure|'' environment should be used for figures. One or
-more images can be placed within a figure. If your figure contains
-third-party material, you must clearly identify it as such, as shown
-in the example below.
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\linewidth]{sample-franklin}
-  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-    Ewing, Inc. [Public domain], via Wikimedia
-    Commons. (\url{https://goo.gl/VLCRBB}).}
-  \Description{The 1907 Franklin Model D roadster.}
-\end{figure}
-
-Your figures should contain a caption which describes the figure to
-the reader. Figure captions go below the figure. Your figures should
-{\bfseries also} include a description suitable for screen readers, to
-assist the visually-challenged to better understand your work.
-
-Figure captions are placed {\itshape below} the figure.
-
-\subsection{The ``Teaser Figure''}
-
-A ``teaser figure'' is an image, or set of images in one figure, that
-are placed after all author and affiliation information, and before
-the body of the article, spanning the page. If you wish to have such a
-figure in your article, place the command immediately before the
-\verb|\maketitle| command:
-\begin{verbatim}
-  \begin{teaserfigure}
-    \includegraphics[width=\textwidth]{sampleteaser}
-    \caption{figure caption}
-    \Description{figure description}
-  \end{teaserfigure}
-\end{verbatim}
-
-\section{Citations and Bibliographies}
-
-The use of \BibTeX\ for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
-
-The bibliography is included in your source document with these two
-commands, placed just before the \linebreak \verb|\end{document}| command:
-\begin{verbatim}
-  \bibliographystyle{ACM-Reference-Format}
-  \bibliography{bibfile}
-\end{verbatim}
-where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
-suffix, of the \BibTeX\ file.
-
-Citations and references are numbered by default. A small number of
-ACM publications have citations and references formatted in the
-``author year'' style; for these exceptions, please include this
-command in the {\bfseries preamble} (before \linebreak
-``\verb|\begin{document}|'') of your \LaTeX\ source:
-\begin{verbatim}
-  \citestyle{acmauthoryear}
-\end{verbatim}
-
-  Some examples.  A paginated journal article \cite{Abril07}, an
-  enumerated journal article \cite{Cohen07}, a reference to an entire
-  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
-  monograph/whole book in a series (see 2a in spec. document)
-  \cite{Harel79}, a divisible-book such as an anthology or compilation
-  \cite{Editor00} followed by the same example, however we only output
-  the series if the volume number is given \cite{Editor00a} (so
-  Editor00a's series should NOT be present since it has no vol. no.),
-  a chapter in a divisible book \cite{Spector90}, a chapter in a
-  divisible book in a series \cite{Douglass98}, a multi-volume work as
-  book \cite{Knuth97}, an article in a proceedings (of a conference,
-  symposium, workshop for example) (paginated proceedings article)
-  \cite{Andler79}, a proceedings article with all possible elements
-  \cite{Smith10}, an example of an enumerated proceedings article
-  \cite{VanGundy07}, an informally published work \cite{Harel78}, a
-  doctoral dissertation \cite{Clarkson85}, a master's thesis:
-  \cite{anisi03}, an online document / world wide web resource
-  \cite{Thornburg01, Poker06}, a video game (Case 1)
-  \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and
-  (Case 3) a patent \cite{JoeScientist001}, work accepted for
-  publication \cite{rous08}, 'YYYYb'-test for prolific author
-  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
-  contain 'duplicate' DOI and URLs (some SIAM articles)
-  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
-  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
-  couple of citations with DOIs:
-  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
-  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}.
-
-\section{Acknowledgments}
-
-Identification of funding sources and other support, and thanks to
-individuals and groups that assisted in the research and the
-preparation of the work should be included in an acknowledgment
-section, which is placed just before the reference section in your
-document.
-
-This section has a special environment:
-\begin{verbatim}
-  \begin{acks}
-  ...
-  \end{acks}
-\end{verbatim}
-so that the information contained therein can be more easily collected
-during the article metadata extraction phase, and to ensure
-consistency in the spelling of the section heading.
-
-Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.
+Além disso, ao envolver os pais e responsáveis no processo 
+educacional por meio do acompanhamento do progresso dos 
+alunos, o software promove uma parceria colaborativa entre 
+escola e comunidade, fortalecendo os laços sociais e a 
+confiança na instituição educacional.
 

### 2024-07-13 Paper.tex
add image
add images

@@
 \title{PAR Digital: Tecnologia em Prol do Ensino Inclusivo}
+% \title{PAR Digital: Tecnologia em Prol da Educação Inclusiva}
 
@@
 para os alunos com deficiência.
+\vspace{0.5cm}
+
+\includegraphics[scale=0.12]{./imgs/capa}
 
@@
 
-% {\bfseries Your document will be returned to you for revision if
-%   modifications are discovered.}
-
 \section{Funcionalidades}
@@
  um papel crucial na promoção de um ambiente inclusivo e eficaz para o
- aprendizado
+ aprendizado.
+\vspace{0.5cm}
+
+\includegraphics[scale=0.12]{./imgs/painel}
 
@@
 estratégias.
-% \begin{verbatim}
-%   \begin{teaserfigure}
-%     \includegraphics[width=\textwidth]{sampleteaser}
-%     \caption{figure caption}
-%     \Description{figure description}
-%   \end{teaserfigure}
-% \end{verbatim}
-% \begin{figure}[h]
-%   \centering
-%   \includegraphics[width=\linewidth]{sample-franklin}
-%   \caption{DANIELE}
-%   \Description{tENTANDO COLOCAR UMA IMAGEM AQUI.}
-% \end{figure}
 
@@
 necessidades específicas de cada aluno.
+\vspace{0.5cm}
+
+\includegraphics[scale=0.12]{./imgs/pei}
 
@@
 implementação do plano e ajudam a monitorar o progresso do aluno.
+\vspace{0.5cm}
+
+\includegraphics[scale=0.12]{./imgs/estrategia}
 
@@
 estratégias estão sendo eficazmente implementadas.
+\vspace{0.5cm}
+
+\includegraphics[scale=0.12]{./imgs/relatorio}
 
@@
 acompanhamento educacional.
+\vspace{0.5cm}
+
+\includegraphics[scale=0.12]{./imgs/forum}
 
@@
 , facilitando a implementação de práticas comprovadamente eficazes.
+\vspace{0.5cm}
+
+\includegraphics[scale=0.12]{./imgs/banco}
 
@@
 dos alunos com necessidades especiais.
+\vspace{0.5cm}
+
+\includegraphics[scale=0.12]{./imgs/materialAdd}
 
@@
  do ensino e a monitorização do desenvolvimento educacional.
+ \vspace{0.5cm}
+
+\includegraphics[scale=0.12]{./imgs/perfil}
 

### 2024-07-15 Paper.tex
add imagem de arquitetura

@@
  fácil e eficiente.
+ \vspace{0.2cm}
+
+ \includegraphics[scale=0.17]{./imgs/arquitetura.png}
 
@@
 
-\section{Appendices}
-
-If your work needs an appendix, add it before the \linebreak
-``\verb|\end{document}|'' command at the conclusion of your source
-document.
-
-Start the appendix with the ``\verb|appendix|'' command:
-\begin{verbatim}
-  \appendix
-\end{verbatim}
-and note that in the appendix, sections are lettered, not
-numbered. This document has two appendices, demonstrating the section
-and subsection identification method.
-
-%%
-%% The acknowledgments section is defined using the "acks" environment
-%% (and NOT an unnumbered section). This ensures the proper
-%% identification of the section in the article metadata, and the
-%% consistent spelling of the heading.
-\begin{acks}
-To Robert, for the bagels and explaining CMYK and color spaces.
-\end{acks}
-
-%%
-%% The next two lines define the bibliography style to be used, and
-%% the bibliography file.
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{sample-base}
-
-%%
-%% If your work has an appendix, this is the place to put it.
-\appendix
-
-\section{Research Methods}
-
-\subsection{Part One}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
-malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
-sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
-vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
-lacinia dolor. Integer ultricies commodo sem nec semper.
-
-\subsection{Part Two}
-
-Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
-ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
-ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
-eros. Vivamus non purus placerat, scelerisque diam eu, cursus
-ante. Etiam aliquam tortor auctor efficitur mattis.
-
-\section{Online Resources}
-
-Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
-pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
-enim maximus. Vestibulum gravida massa ut felis suscipit
-congue. Quisque mattis elit a risus ultrices commodo venenatis eget
-dui. Etiam sagittis eleifend elementum.
-
-Nam interdum magna at lectus dignissim, ac dignissim lorem
-rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
-massa et mattis lacinia.
+\section{Conclusão e Trabalhos Futuros}
+TODO:Fazer fechamento do artigo e direções de funcionalidades futuras
 
